<!--
%\VignetteEngine{knitr::docco_linear}
%\VignetteIndexEntry{The intsvy PIAAC examples}
-->

# Installation

First you need to download intsvy package from eldafani github repository
and PIAAC package with piaac data from pbiecek repository.

```{r, message=FALSE}
library(devtools)
library(reshape)
library(ggplot2)
if (!require(intsvy)) {
  install_github("eldafani/intsvy")
#  install_github("pbiecek/intsvy")
}
if (!require(PIAAC)) {
  install_github("pbiecek/PIAAC")
}

dim(piaac)
```

# Proficiency levels

The piaac.ben.pv() function calculates proportions of groups defined by 'cutoff' over selected PVin stratus defined by 'by' variables. The 'data' argument should be a data frame with column SPFWT0 (final weights in PIAAC) and SPFWT.. for BRR weights.

```{r}

#Table A2.5      											
#Percentage of adults scoring at each proficiency level in numeracy														
piaac.ben.pv(pvlabel="NUM", by="CNTRYID", data=piaac)

#Table A2.1
#Percentage of adults scoring at each proficiency level in literacy  													
piaac.ben.pv(pvlabel="LIT", by="CNTRYID", data=piaac)

```
