<!--
%\VignetteEngine{knitr::docco_linear}
%\VignetteIndexEntry{The intsvy PIAAC examples}
-->

# Installation

First you need to download intsvy package from eldafani github repository
and PIAAC package with piaac data from pbiecek repository.

```{r, message=FALSE}
library(devtools)
library(reshape)
library(ggplot2)
if (!require(intsvy)) {
  install_github("eldafani/intsvy")
#  install_github("pbiecek/intsvy")
}
if (!require(PIAAC)) {
  install_github("pbiecek/PIAAC")
}

dim(piaac)
```

# Contingency tables

The piaac.table() function calculates proportions of groups defined by 'variable' in stratus defined by 'by' variables. The 'data' argument should be a data frame with column SPFWT0 (final weights in PIAAC) and SPFWT.. for BRR weights.

```{r}

# age distribution in whole dataset
(ptable <- piaac.table(variable="AGEG10LFS", data=piaac))
# age distribution within countries
head(ptableC <- piaac.table(variable="AGEG10LFS", by="CNTRYID", data=piaac))
# age distribution within countries and gender segments
head(ptableCA <- piaac.table(variable="AGEG10LFS", by=c("CNTRYID", "GENDER_R"), data=piaac))

```

The output of piaac.table() function is of the class intsvy.table and plot() is one of overloaded functions for this class. 

```{r}
# age distribution in whole dataset
plot(ptable)

# age distribution within countries
plot(ptableC, stacked=TRUE)

# age distribution within countries and gender segments
plot(na.omit(ptableCA), stacked=TRUE)

```

# Averages and group averages for plausible values

The piaac.mean.pv() function calculates averages of variable 'pvlabel' in stratus defined by 'by' variables. The 'data' argument should be a data frame with column SPFWT0 (final weights in PIAAC) and SPFWT.. for BRR weights.

Note that 'pvlab' is one of 'LIT' (for literacy), 'NUM' (for numeracy), 'PSL' (for problem solving). In piaac data there are 10 plausible values for each of these dimensions.

```{r}
#Table A2.2a from SkillsOutlook2013_ENG_Table_Chapter2

# Country averages
head(pmeansNC <- piaac.mean.pv(pvlabel="NUM", by="CNTRYID", data=piaac, export=FALSE))
# Country averages for different age groups
head(pmeansNCA <- piaac.mean.pv(pvlabel="NUM", by=c("CNTRYID", "AGEG10LFS"), data=piaac, export=FALSE))
# Country averages for different age and gender groups
head(pmeansNCAG <- piaac.mean.pv(pvlabel="NUM", by=c("CNTRYID", "AGEG10LFS", "GENDER_R"), data=piaac, export=FALSE))
# Country averages for different age and gender groups (changed order)
head(pmeansNCGA <- piaac.mean.pv(pvlabel="NUM", by=c("CNTRYID", "GENDER_R", "AGEG10LFS"), data=piaac, export=FALSE))

```

The output of piaac.mean.pv() function is of the class intsvy.mean and plot() is one of overloaded functions for this class. 

```{r}
#
# plotting country average NUM performance 
plot(pmeansNC) + ggtitle("Country performance in NUM")
# without se bars, not good idea
plot(pmeansNC, se=FALSE)
# sorted, thats better
plot(pmeansNC, sort=TRUE)

#
# plotting country average within 
# age groups NUM performance 
plot(pmeansNCA, sort=TRUE)
#
# plotting country average within 
# age and gender groups NUM performance 
plot(na.omit(pmeansNCGA), sort=TRUE)

```

# Averages and group averages part 2

The piaac.mean() function calculates averages of 'variable' in groups defined by 'by' variables. The 'data' argument should be a data frame with column SPFWT0 (final weights in PIAAC) and SPFWT.. for BRR weights.

Note that 'variable' should be continuous and should not be any of plausible values (there is a separate function piaac.mean.pv() for them).

```{r}
# average age in different countries
head(pmeansAC <- piaac.mean(variable="AGE_R", by="CNTRYID", data=piaac, export=FALSE))

# average age in different countries and for differet genders
head(pmeansACG <- piaac.mean(variable="AGE_R", by=c("CNTRYID","GENDER_R"), data=piaac, export=FALSE))

```

As for piaac.mean.pv() also for piaac.mean() the output is of the class intsvy.mean and plot() is overloaded for it. 

```{r}
plot(na.omit(pmeansAC), sort=TRUE)
plot(na.omit(pmeansACG), sort=TRUE)
```


# Regression models with plausible values

The piaac.reg.pv() function runes linear regression model with 'pvlabel' as an dependent variable and variables 'x' as independent variables. Regression models are calculated in stratus defined by 'by' variables. The 'data' argument should be a data frame with column SPFWT0 (final weights in PIAAC) and SPFWT.. for BRR weights.

Note that 'pvlab' is one of 'LIT' (for literacy), 'NUM' (for numeracy), 'PSL' (for problem solving). In piaac data there are 10 plausible values for each of these dimensions.


```{r}
#
# LITeracy explained by GENDER in different countries
rmodelLG <- piaac.reg.pv(pvlabel="LIT", x="GENDER_R", by = "CNTRYID", data=piaac, export=FALSE) 
rmodelLG[1:3]
#
# LITeracy explained by GENDER and level of trust in different countries
rmodelLGI <- piaac.reg.pv(pvlabel="LIT", x=c("GENDER_R", "I_Q06A"), by = "CNTRYID", data=piaac, export=FALSE) 
rmodelLGI[1:3]

```

The piaac.mean.pv() function outputs an object of intsvy.reg class with overloaded plot() function. 

```{r}
# add se intervals
plot(rmodelLG, se=TRUE)
# sorted along R square
plot(rmodelLG, se=TRUE, sort=TRUE)
```

```{r, fig.height=15}
plot(rmodelLGI, se=TRUE)
```


# Regression models part 2

The piaac.reg() function fits regression models with 'y' as dependent variable and 'x' as independent variables and groups defined by 'by' variables. The 'data' argument should be a data frame with column SPFWT0 (final weights in PIAAC) and SPFWT.. for BRR weights.

Note that 'variable' should be continuous and should not be any of plausible values (there is a separate function piaac.reg.pv() for them).


```{r}
#
# regression GENDER on AGE per country
rmodelAGC <- piaac.reg(y="AGE_R", x="GENDER_R", by="CNTRYID", data=piaac, export=FALSE) 

```

As for piaac.reg.pv() also for piaac.reg() the output is of the class intsvy.reg and plot() is overloaded for it. 

```{r}
plot(rmodelAGC, se=TRUE)
# sorted along R square
plot(rmodelAGC, se=TRUE, sort=TRUE)
```

