---
title: "Examples with PIRLS 2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
library("devtools")
install_github("eldafani/intsvy")
library("intsvy")
```

```{r, echo = FALSE}
library("intsvy")
dir <- "/home/eldani/eldani/International LSA/PIRLS/PIRLS 2021/3_International Database/1_SPSS Data/"
```

## Read data for selected variables and countries
The object *dir* specifies the directory path where the PIRLS 2021 data is located (eg. "/home/data").
Variable selection can be done with aid of *pirls.var.label(dir)*.

```{r}
pirls <- pirls.select.merge(folder= dir,
                            student= c("ITSEX", "ASBG03"),
                            home= c("ASBHSES", "ASDHSES"), 
                            school= c("ACBG05B"))
```

## Calculate average reading score by country
```{r}
pirls.mean.pv(pvlabel = paste0("ASRREA0", 1:5), by = "IDCNTRYL", data = pirls)
```

## Calculate average reading score by country and sex
```{r}
pirls.mean.pv(pvlabel = paste0("ASRREA0", 1:5), by = c("IDCNTRYL", "ITSEX"), 
              data = pirls[!is.na(pirls$ITSEX), ])
```

### Calculate MPL by country

```{r}
pirls.ben.pv(pvlabel= paste0("ASRREA0", 1:5), cutoff = 400, by="IDCNTRYL", data=pirls)
```

## Estimate regression of reading on sex by country
```{r}
pirls.reg.pv(pvlabel= paste0("ASRREA0", 1:5), x="ITSEX", by = "IDCNTRYL", data=pirls[!is.na(pirls$ITSEX), ])
```



