---
title: "Examples with PISA 2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("intsvy")
dir <- "/home/eldani/eldani/International LSA/PISA/2022"
```

```{r, eval=FALSE}
library("devtools")
install_github("eldafani/intsvy")
library("intsvy")
```


## Select data
Check names of variables in student and school files and names of participating countries for data selection. Datasets are stored in directory, *dir*. 

```{r, eval=FALSE}
pisa.var.label(folder = dir,
               student.file="CY08MSP_STU_QQQ.sav",
               school.file="CY08MSP_SCH_QQQ.sav", output = dir)
```


Select data for three countries, student's SES, sex, and school's location
```{r}

pisa <- pisa.select.merge(folder = dir,
                          student.file="CY08MSP_STU_QQQ.sav",
                          school.file="CY08MSP_SCH_QQQ.sav",
                          student= c("ESCS", "ST004D01T"),
                          school = c("SC001Q01TA"), 
                          countries = c("ARG", "FRA", "PER"))
```

## Calculate average mathematics score by country
The average mathematics score and its associated standard error are presented, first for Argentina, second for France and third for Peru.

```{r}
pisa.mean.pv(pvlabel = paste0("PV", 1:10, "MATH"), by = "CNT", data = pisa)
```

## Calculate average mathematics score by country and sex
```{r}
pisa.mean.pv(pvlabel = paste0("PV", 1:10, "MATH"), by = c("CNT", "ST004D01T"), data = pisa)
```

## Calculate proficiency levels by country

### Cutoff scores for mathematics performance

```{r}
mathcut <- c(357.77, 420.07, 482.38, 544.68, 606.99, 669.3)
```

### Produce table with results
```{r}
pisa.ben.pv(pvlabel= paste0("PV", 1:10, "MATH"), cutoff= mathcut, by="CNT", data=pisa)
```

## Estimate regression of reading on sex by country
```{r}
pisa.reg.pv(pvlabel= paste0("PV", 1:10, "READ"), x="ST004D01T", by = "CNT", data=pisa)
```

## Estimate regression of mathematics on SES by country
```{r}
pisa.reg.pv(pvlabel= paste0("PV", 1:10, "MATH"), x="ESCS", by = "CNT", data=pisa)
```


