---
title: "Examples with TIMSS 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eval = FALSE}
library("devtools")
install_github("eldafani/intsvy")
library("intsvy")
```

```{r echo=FALSE}
options(width=120)
```

```{r echo=FALSE}
library("intsvy")
dir <- "/home/eldani/eldani/International LSA/TIMSS/TIMSS 19/Grade 4"
```

## Grade 4
### Read data
The object dir specifies the directory path where the TIMSS 2019 data is located (eg. “/home/data”).
Variable selection can be done with aid of timssg4.var.label(dir)

```{r}
timss <- timssg4.select.merge(folder= dir,
         student= c("ITSEX", "ASBG05A", "ASBG05B", "ASBG05C", "ASBG05D",
                    "ASBG03"), 
         home= c("ASBH14", "ASBH10", "ASDHEDUP", "ASDHOCCP", "ASBH17A", "ASBH17B"),
         school= c("ACBG05B"), 
         countries = c("ARE", "CHL", "CAN", "HUN"))
```

### Calculate mean math performance by education system
```{r}
timss.mean.pv(pvlabel=paste0("ASMMAT0", 1:5), by= "IDCNTRYL", data=timss)
```

### Calculate mean math performance by education system and student's sex
```{r}
timss.mean.pv(pvlabel= paste0("ASMMAT0", 1:5), by= c("IDCNTRYL", "ITSEX"), data=timss)
```

### International benchmarks by education system
```{r}
intsvy.ben.pv(pvnames= paste0("ASMMAT0", 1:5), cutoff =   c(400, 475, 550, 625), 
              by= c("IDCNTRYL", "ITSEX"), data=timss, config = timss4_conf)
```


### International benchmarks by education system and student's sex
```{r}
intsvy.ben.pv(pvnames= paste0("ASMMAT0", 1:5), cutoff =   c(400, 475, 550, 625), 
              by= c("IDCNTRYL", "ITSEX"), data=timss, config = timss4_conf)
```

